Proposal: Influences of GDP in the U.S

### 2022-10-09 Proposal/Proposal.tex
commit
commit #adding notes

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% meta data

@@

\paragraph{Introduction}
%Introduction: Introducing the topic and why you have chosen this topic (3–5 lines). 
%Mention briefly the current related research and cite relevant works.
Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
It is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
GDP is the total monetary value of all goods and services that are produced in a country. For this paper, I will focus solely on the GDP in the United States. 
\citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP. They also found that inflation is highly correlated, but not a significant influencer.

@@

\paragraph{Data}
My data has been collected from the Federal Reserve Economic Data (FRED) website.
All of the datasets have been collected seperately and compiled into one dataset. 
There are seven variables and sixty seven observations in this dataset. 
My dependent variable is Gross Domestic Product (GDP). 
My independent variables are Population (POP), Nominal Broad U.S Dollar Index (NBUSDI), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Business Sector Labor Productivity (BSLP). 
The dataset contains quarterly observations starting from January 1st, 2006 up until July 7th, 2022.
The limited amount of data comes from Nominal Broad U.S Dollar Index (NBUSDI) only starting to be recorded by FRED in 2006.

@@

\paragraph{Discussion}
I expect to find that many of my variables will have a strong relationship with GDP.
Mainly, I expect Disposable Personal Income (DPI) and Unemployment Rate (UNRATE) to have the strongest relationships since person consumption and high goverment costs impact GDP.
I am interested in testing Nominal Broad U.S Dollar Index (NBUSDI) because this varible measures the U.S. dollar compared with all other currencies. 
This variable is assocated with exports which is used when calculating GDP.
I am also interested in testing Business Sector Labor Productivity (BSLP). GDP is a measure of labor productivity, so I am expecting BSLP to have a strong relationship with GDP.

>>>>

%% preamble
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

% highlighting hyper links and refrences 
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

% Need to research how to properly cite websites

@@

\paragraph{Introduction}
%Introduction: Introducing the topic and why you have chosen this topic (3–5 lines). 
%Mention briefly the current related research and cite relevant works.
Gross Domestic Product is one of the main factors that goes into determining a countries economic growth. 
GDP is the total monetary value of all goods and services that are produced in a country and is a "comprehensive measure of U.S economic activity" \citet[]{bea}.
For this paper, I will focus solely on the GDP in the United States. 
\citet{divya2014study} found that exchange rates and market indexes are important factors that influence an economies GDP. They also found that inflation is highly correlated, but not a significant influencer.

@@

%ask if should use dif variables w more observations
\paragraph{Data}
My data has been collected from the Federal Reserve Economic Data (FRED) website.
The data from the FRED website is collected and updated by the Research Department at the Federal Reserve Bank of St. Louis. 
All of the datasets used in this analysis have been collected seperately and compiled into one dataset. 
There are seven variables and sixty seven observations in this dataset. 
My dependent variable is Gross Domestic Product (GDP). 
My independent variables are Population (POP), Nominal Broad U.S Dollar Index (NBUSDI), 10 Year Treasury Constant Maturity Rate (TCMR), Disposable Personal Income (DPI), Unemployment Rate (UNRATE), and Business Sector Labor Productivity (BSLP). 
The dataset contains quarterly observations starting from January 1st, 2006 up until July 7th, 2022.
The limited amount of data comes from Nominal Broad U.S Dollar Index (NBUSDI) only starting to be recorded by FRED in 2006.

@@

\paragraph{Discussion}
I expect to find that many of my variables will have a strong relationship with GDP.
Mainly, I expect Disposable Personal Income (DPI) and Unemployment Rate (UNRATE) to have the strongest relationships since personal consumption and high goverment costs impact GDP.
I am interested in testing Nominal Broad U.S Dollar Index (NBUSDI) because this varible measures the U.S. dollar compared with all other currencies. 
This variable is assocated with exports which is used when calculating GDP.
I am also interested in testing Business Sector Labor Productivity (BSLP). GDP is a measure of labor productivity, so I am expecting BSLP to have a strong relationship with GDP.
